% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage[T1]{fontenc}
\usepackage{charter}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{tabularx}
\usepackage[compact, explicit]{titlesec}
\usepackage{ulem}
\usepackage{enumitem}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
%\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Ben Berger}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9in},
  top=1in
}

\pagenumbering{gobble}


\titleformat{\section}{\Large\bfseries}{\thesection}{1em}{#1}
\titlespacing*{\section}{0pt}{*0}{0pt}
\titleformat{\subsection}{\large}{\thesection}{1em}{\uline{#1}}
\titlespacing*{\subsection}{0pt}{*0}{.25em}


% Customize page headers
%\pagestyle{myheadings}
%\markright{\name}
%\thispagestyle{empty}

% Custom section fonts
%\usepackage{sectsty}
%
%\sectionfont{\rmfamily\bfseries\Large}
%\subsectionfont{\underline\normalfont\fontfamily{phv}\bfseries}
%
%\renewcommand\section{\@startsection {section}{1}{\z@}%
%	{-3.5ex \@plus -1ex \@minus -.2ex}%
%	{2.3ex \@plus.2ex}%
%	{\normalfont\Large\bfseries\SS@sectfont}}
%\renewcommand\subsection{\@startsection{subsection}{2}{\z@}%
%	{-3.25ex\@plus -1ex \@minus -.2ex}%
%	{1.5ex \@plus .2ex}%
%	{\normalfont\large\bfseries\SS@subsectfont}}
%\sectionfont{\bfseries} % <---- omitting \bfseries still gives bold font


% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}





% Make lists without bullets
%\renewenvironment{itemize}{
%  \begin{list}{}{
%    \setlength{\leftmargin}{0em}
%  }
%}{
%  \end{list}
%}
\setlist[itemize]{itemsep=0em, parsep=0pt, topsep=0pt, label={}, leftmargin=0em}


\begin{document}

% Place name at left
%{\huge \bf \name}

% Alternatively, print name centered and bold:
\centerline{\huge \bf \name}

\vspace{2em}

\begin{minipage}{0.45\linewidth}
  \href{http://www.hks.harvard.edu/}{John F. Kennedy School of Government} \\
  Harvard University \\
  79 John F. Kennedy Street \\
  Cambridge, MA 02138
\end{minipage}
%
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Email: & \href{mailto:benjamin\_berger@hks.harvard.edu}{\bf benjamin\_berger@hks.harvard.edu} \\
    Homepage: & \href{http://ben-berger.com/}{\bf ben-berger.com} 
  \end{tabular}
\end{minipage}

\vspace{.25em}
\hrule
\vspace{.5em}

\section*{Education}

\begin{itemize}
  \item Ph.D. in Public Policy (Economics Track), Harvard University, May 2024 (expected)
  \item B.A. in Economics and Mathematics, University of Miami, \textit{magna cum laude}, 2016
\end{itemize}

\section*{Research Interests}
Health Economics, Innovation, Industrial Organization 

\section*{Research Experience}
\begin{tabularx}{\linewidth}{@{} l X }
	05/2019 -- 08/2019 & Graduate Research Assistant to Amitabh Chandra, Harvard Kennedy School \\
	05/2019 -- 08/2019 & Graduate Research Assistant to Nicole Maestas, Harvard Medical School \\
	07/2016 -- 08/2018 & Full-Time Research Assistant to Amitabh Chandra, National Bureau of Economic Research \\
	06/2015 -- 08/2015 & Research Intern, International Council of Shopping Centers \\
	01/2015 -- 06/2015 & Undergraduate Research Assistant to Chris Parmeter, University of Miami
\end{tabularx} \\

\section*{Publications}
\subsection*{Working Papers}
\begin{itemize}
	\item ``Regulatory Approval and Expanded Market Size.'' NBER Working Paper, 2021. \textit{(with Amitabh Chandra and Craig Garthwaite).}
\end{itemize}

\subsection*{Book Chapters}
\begin{itemize}
	\item ``The Link between Health and Working Longer: Differences in Work Capacity.'' In Overtime: America's Aging Workforce and the Future of ``Working Longer''. The Alfred P. Sloan Foundation, 2022. \textit{(with Italo Lopez-Garcia, Nicole Maestas, and Kathleen Mullen).}
	
	\item ``The Orphan Drug Act at 35: An Outlook for the 21st Century.'' In Innovation Policy and the Economy, Volume 19. University of Chicago Press, 2018. \textit{(with Nicholas Bagley, Amitabh Chandra, Craig Garthwaite, and Ariel Dora Stern).}
\end{itemize}

\section*{Teaching Experience}
\begin{tabularx}{\linewidth}{@{}l X}
	Fall 2022 & Teaching Fellow, Empirical Methods I, Master's Level, Harvard Kennedy School \\
	Spring 2021 -- 2022 & Teaching Fellow, Empirical Methods II, Master's Level, Harvard Kennedy School \\
	& Overall Effectiveness: 4.85/5 (average among TFs: 4.42)\\
	& Selected feedback: \textit{I can't believe this is Ben's first time teaching --- he's incredibly good at it and I hope he continues for a long time!} \\
	& \textit{Ben is wonderful --- he is so helpful and takes a lot of time to make sure that you understand difficult concepts and that he answers questions clearly and comprehensively.}
\end{tabularx}


\section*{Fellowships and Scholarships}
\begin{itemize}
	\item NSF Graduate Research Fellowship, Awarded (2019).
	\item NSF Graduate Research Fellowship, Honorable Mention (2018).
	\item Dickinson Merit Scholarship, University of Miami, Awarded (2012).
\end{itemize}

\section*{Personal}
%
%\begin{itemize}
%\item Born July 17, 1994.
United States Citizen
%\end{itemize}




%\subsection*{Journal Articles}
%
%\begin{itemize}
%\item A General Mathematical Theory of Depreciation, 1929, {\it Journal
%    of The American Statistical Association} 20, 340--353.
%\item Differential Equations Subject to Error, 1927, {\it Journal of The
%    American Statistical Association}.
%\item Applications of the Theory of Error to the Interpretation of
%  Trends (with H. Working), 1929, {\it Journal of the American
%    Statistical Association}.
%\end{itemize}
%
%\subsection*{Proceedings}
%
%\begin{itemize}
%\item A generalized T-Test and measure of multivariate dispersion,
%  Proc. Second Berkeley Symposium of Mathematical Statistics and
%  Probability, 1951.
%\end{itemize}



\bigskip


% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}
